Hydras, Ordinals \& Co. \\ A library in Coq of entertaining formal mathematics

### 2021-10-04 doc/JFLA2022/paper.tex
remove a few TODOs[pierre]

\begin{itemize}
\item formalizations of mathematics in proof assistants, such as Coq, continually grow in size and scope
\begin{itemize}
\item the Mathematical Components library and the four-color theorem and the odd order theorem in Coq
\item the Mathlib library for Lean
\end{itemize}
\item to continue to be useful as examples and reusable libraries, formalizations must be well \emph{documented} and \emph{maintained} to ensure they work with new proof assistant releases \TODO[Pierre]{add evolution of styles of proof and formalization (not limited to Coq litterature)? } 
\item Lean and Mathematical Components have accompanying books, which are written mainly to onboard new library users
\item book authors faced with several design choices: literate documents, using tools to keep the book and the proof assistant synchronized
\end{itemize}

@@

Originally, we copied snippets from Coq sources into LaTeX manually, and recorded and inserted the corresponding outputs manually as well.  This approach is common, but brittle: changes to Coq definitions or lemmas had to be reflected in the book's sources, and we found multiple instances where the book and the Coq development had diverged (see FIXME cite alectryon for a discussion of various approaches to documentation of Coq developments).

@@

\begin{todo}
  Interest of Alectryon:
  \begin{itemize}
  \item \TODO[Pierre]{the order of appearance of snippets in the book is independent from the module structure}
   \item \TODO[Pierre]{Slicing our proofs into snippets allowed to show only the main parts of our proofsleaved with text (Figure~\ref{fig:Ex42-schutte}).}

  \end{itemize}

\end{todo}

>>>>

\begin{itemize}
\item formalizations of mathematics in proof assistants, such as Coq, continually grow in size and scope
\begin{itemize}
\item the Mathematical Components library and the four-color theorem and the odd order theorem in Coq
\item the Mathlib library for Lean
\end{itemize}
\item to continue to be useful as examples and reusable libraries, formalizations must be well \emph{documented} and \emph{maintained} to ensure they work with new proof assistant releases. %\TODO[Pierre]{add evolution of styles of proof and formalization (not limited to Coq litterature)? } 
\item Lean and Mathematical Components have accompanying books, which are written mainly to onboard new library users
\item book authors faced with several design choices: literate documents, using tools to keep the book and the proof assistant synchronized
\end{itemize}

@@

Originally, we copied snippets from Coq sources into LaTeX manually, and recorded and inserted the corresponding outputs manually as well.  This approach is common, but brittle: changes to Coq definitions or lemmas had to be reflected in the book's sources, and we found multiple instances where the book and the Coq development had diverged. \TODO[Clément]{see FIXME cite alectryon for a discussion of various approaches to documentation of Coq developments}

@@
